%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Shane Waxler} \\ \vspace{1pt}
    \small 858-444-7997 $|$ \href{mailto:shanewaxler1@gmail.com}{\underline{Email}} $|$ 
    \href{https://www.linkedin.com/in/shane-waxler-b205891b9/}{\underline{Linkedin}} $|$
    \href{https://github.com/qherm}{\underline{GitHub}} $|$
    \href{54.193.167.39}{\underline{Portfolio}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Francisco State University}{San Francisco, CA}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{August 2018 - May 2022}
          \resumeItemListStart
            \resumeItem{\emph{Graduated magna cum laude}}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Software Developer Intern}{March 2019 -- August 2020}
    {Universal Financial Consultants}{San Diego, CA}
    \resumeItemListStart
      \resumeItem{Developed an executable Python application to enable user-friendly management of public data for \\ asset allocation models, automating the selection process for improved portfolio performance.}
      \resumeItem{Wrote an informational/portfolio \MYhref{https://www.barrywaxler.com/}{website} for UFC in HTML, CSS, and Javascript.}
    \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant - CSC 865: Graduate Level Artificial Intelligence}{November 2021 –- May 2022}
      {SFSU - Computer Science Department}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Wrote an \MYhref{https://github.com/qherm/csc865-autograding-tools}{autograder} script in Python which gives verbose grade/plagiarism analyses for each assignment,  \\ thereby eliminating the need to hire graders in the future and saving 30+ paid hours per month.}
        \resumeItem{Host weekly office hours and online help for class-related material.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Machine Learning Researcher}{August 2021 -- February 2022}
      {PeRL at SFSU}{San Francisco, CA}
      \resumeItemListStart
      \resumeItem{Effectively predicted user-perception ratings of robot hands via a linear regression model.}
      \resumeItem{Wrote a website in HTML/CSS allowing research/robotics teams to use our model to predict how users will react to their proposed robot hand design.}
      \resumeItem{Gathered data from 200+ paid surveys via Amazon Mechanical Turk to train the regression model.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Elementary/Middle School Computer Science Instructor}{August 2021 -- January 2022}
      {C.R.E.W.}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Write engaging curriculum to engage and motivate young students in a voluntary after-school computer science program.}
        \resumeItem{Lead classroom environments with students of varying age and familiarity with programming concepts.}
        \resumeItem{Middle school students were taught Javascript. Elementary school students were taught Blocks.}
      \resumeItemListEnd
      
      
     
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\MYhref{http://ec2-35-168-3-139.compute-1.amazonaws.com/}{GatorMart} - Marketplace for SFSU Faculty and Students}  \\ Technologies: \emph{Node, Express, Handlebars, MySQL, AWS}}{Sep. 2021 -- Dec. 2021 }
        \resumeItemListStart
          \resumeItem{Successfully led a team of 8 members using Agile methodology to build and ship a safe, secure, and appealing marketplace for SFSU students.}
          \resumeItem{Assisted in the majority of backend (using MVC architecture) and frontend development.}
        \resumeItemListEnd


      \resumeProjectHeading
          {\textbf{\MYhref{https://github.com/qherm/notuno}{Notuno} - Multiplayer Online Uno Card Game} \\ Technologies: \emph{Node, Express, PostgreSQL, Heroku}}{Sep. 2021 -- Dec. 2021 }
          \resumeItemListStart
            \resumeItem{Wrote the backend for an online multiplayer game from scratch using Javascript and SQL.}
            \resumeItem{Worked as full-time team-lead for a four-person team. Instructed them on working with large codebases.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{\MYhref{https://github.com/qherm/multithreaded-webserver-java}{Multithreaded Webserver}} \\ Technologies: \emph{Java}}{January 2021 -- March 2021}
          \resumeItemListStart
            \resumeItem{Wrote a functioning Apache-esque webserver from scratch without the assistance of any HTTP libraries.}
          \resumeItemListEnd
         

    \resumeSubHeadingListEnd


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Javascript/Typescript, Java, C, SQL, HTML/CSS} \\
     \textbf{Frameworks/Libraries}{: Tensorflow, Keras, NumPy, SymPy, Express.js} \\
     \textbf{Developer Tools/Software}{: GitHub, Linux/Unix, Node.js, MySQL, Apache HTTP Server} \\
     \textbf{Platforms}{: AWS, Amazon Mechanical Turk, Heroku}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
